Estimating the incidence of SARS-CoV-2 from prevalence data

### 2023-07-12 thesis.tex
First pass editing problem section
Done:
- Restructuring section so that it makes sense
- Majority of edits to section (see below)

Still outstanding:
- Edit pargraph introducting survival analysis
- Edit from "few studies" onwards
- Reread whole section for flow and clarity

@@

\section{Incidence, prevalence, and duration}

\section{Studies used in this thesis} \label{intro:sec:studies}

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

\subsection{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

@@

>>>>

\chapter{Incidence, prevalence, and duration}
We wish to estimate the distribution of time for which an individual is positive for.
An individual could have multiple infections, and hence I refer to \emph{infection episodes}.

I define an individual as \emph{detectable} if they would test positive if tested, in the absence of misclassification error (which is dealt with in \cref{E-imperf-test}).
Episode $i$'s \emph{duration of positivity}, $D_i$ is the number of days that they are detectable for; I use time discretised to days, therefore, the duration is at least 1 day.
Note that the relationship between positivity (\ie the result of a PCR test) and infectiousness (\ie an individual's ability to pass on the virus) is complex~\autocites{lascolaViral}{singanayagamDuration}, and beyond the scope of this thesis.
I define an episode as starting at time $B_i$ and ends at $E_i$, hence $D_i = E_i - B_i + 1$.

An episode is \emph{detected} when they test positive at least once, if this occurs; episode $i$ is detected at time $t$ if and only if: $i$ is detectable at $t$, $i$ is tested at $t$, and the test returns positive (a false negative does not occur).

The survival time function, parameterised by $\theta$, is the probability that an episode lasts at least $t$ days: $S_\theta(t) = \prob(D_i \geq t \mid B_i = b, \theta)$, where $D_i$ and $B_i$ are the duration and starting time of episode $i$ respectively.
I make the standard assumption that $D_i$ and $B_i$ are independent and hence: $S_\theta(t) = \prob(D_i \geq t \mid \theta)$.I utilise survival analysis for analysing this data.
Survival analysis is the area of statistics concerned with estimating the distribution of the times between events.
It is broadly applicable to many domains, such as the time-to-failure for a mechanical system or the effect of a treatment on time spent in hospital.
In the context of this thesis, the distribution to estimate is that of duration of positivity.
The \emph{initiating event} is when the duration starts, \ie becoming detectable.
The \emph{terminating event} is when the duration ends, \ie becoming no longer detectable.

\chapter{Studies used in this thesis} \label{intro:sec:studies}

@@

\section{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

\section{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

@@

Consider the CIS data.
It consists of a series of tests on the same individuals (longitudinal data), where some individuals have a series of positive tests.
